Concurrent Programming in Harmony

### 2022-01-10 book/paper.tex
Implemented setintlevel in TLA+
All except trap...
Latest

A formal specification of the Harmony Virtual Machine is well underway but
not yet completed.  At this time, there is no support yet for bitwise integer
operations.
Also, strings are limited to the printable characters minus
double quotes, back quotes, or backslashes.
Given a Harmony program, you can output the TLA+ specification for
the program using the following command:

@@

First and foremost I would like to thank my student Haobin Ni with
whom I've had numerous discussions about the design of Harmony.
Haobin even contributed some code to the Harmony compiler.

Kevin Sun and Anthony Yang built a beautiful VSCode extension for Harmony
called HarmonyLang and proceeded to build an animator for Harmony
executions and two cloud-based Harmony offerings, which you can learn
about at \url{http://harmony.cs.cornell.edu}.  They also developed much of
that web site.  Later they were joined by Shi Chong Zhao, who also
made significant contributions.

@@

Leslie Lamport introduced me to using model checking to test properties
of a concurrent system.  My experimentation with using TLC on Peterson's
Algorithm became an aha moment for me.

I first demonstrated Harmony to the students in my CS6480 class on systems
and formal verification and
received valuable feedback from them.

The following people contributed by making comments on or finding bugs in
early drafts of the book:
Alex Chang,
Anneke van Renesse,
Brendon Nguyen,
Hartek Sabharwal,
Heather Zheng,
Jack Rehmann,
Jacob Brugh,
Liam Arzola,
Lorenzo Alvisi,
Maria Martucci,
Phillip O'Reggio,
Saleh Hassen,
Sunwook Kim,
Terryn Jung,
Trishita Tiwari,
William Ma,
Xiangyu Zhang,
Yidan Wang,
Zhuoyu Xu,
and
Zoltan Csaki.

>>>>

A formal specification of the Harmony Virtual Machine is well underway but
not yet completed.  In particular, <{trap}> is not yet specified.
Also, strings are limited to the printable characters minus
double quotes, back quotes, or backslashes.
But everything else is specified.
Given a Harmony program, you can output the TLA+ specification for
the program using the following command:

@@

First and foremost I would like to thank my student Haobin Ni with
whom I've had numerous discussions about the initial design of Harmony.
Haobin even contributed some code to the Harmony compiler.
Many thanks are also due to William Ma who refactored the Harmony code
to make it easier to maintain.
He also wrote the first version of the behavior automaton generator
and created the first graphs using the graphviz tool.
I have had lots of discussions with him about a wide range of
improvements to the Harmony language, many of which came to fruition.
I also want to thank Ariel Kellison with whom I discussed approaches
to formally specify the Harmony virtual machine in TLA+.

Kevin Sun and Anthony Yang built a beautiful VSCode extension for Harmony
called HarmonyLang and proceeded to build an animator for Harmony
executions and two cloud-based Harmony offerings, which you can learn
about at \url{http://harmony.cs.cornell.edu}.  They also developed much of
that web site and made valuable suggestions for improvements to the
Harmony language.  Later they were joined by Shi Chong Zhao, who also
made significant contributions.  Kevin and Anthony continue to make
great contributions to the Harmony distribution.

@@

Leslie Lamport introduced me to using model checking to test properties
of a concurrent system.  My experimentation with using TLC on Peterson's
Algorithm became an aha moment for me.  I have learned so much from his
papers.

I first demonstrated Harmony to the students in my CS6480 class on systems
and formal verification and received valuable feedback from them.
The following people contributed by making comments on or finding bugs in
early drafts of the book:
Alex Chang,
Anneke van Renesse,
Brendon Nguyen,
Hartek Sabharwal,
Heather Zheng,
Jack Rehmann,
Jacob Brugh,
Liam Arzola,
Lorenzo Alvisi,
Maria Martucci,
Phillip O'Reggio,
Saleh Hassen,
Sunwook Kim,
Terryn Jung,
Trishita Tiwari,
Xiangyu Zhang,
Yidan Wang,
Zhuoyu Xu,
and
Zoltan Csaki.
